Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-16 numerical-mhd-ct.tex
fixing refs. again.

This MHD method was developed by \citet{Collins10} in order to study Population
III stars \citep{Xu08}, molecular clouds \citep{collins12}, and galaxy clusters
\citep{Xu12, Skillman13}.  A full description and suite of test problems can be
found in \citet{Collins10}

>>>>

This MHD method was developed by \citet{Collins10} in order to study Population
III stars \citep{Xu08}, molecular clouds \citep{Collins12a}, and galaxy clusters
\citep{Xu12, Skillman13}.  A full description and suite of test problems can be
found in \citet{Collins10}
